### 2017-04-12 paper/sexSelectionSpacing-ver1.tex
Edit first part of introduction

Understanding and measuring son preference has been an important research 
area for decades and is as salient as ever.
India, for example, has seen dramatic increases in the males-to-females ratio 
at birth over the last three decades as access to prenatal sex determination 
expanded.%
\footnote{
See \citet{das_gupta97}, \citet{Sudha1999},
\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
India is not alone; both China and South Korea saw
significant changes in the sex ratio at birth \citep{Yi1993,park95}.
}
Recent research suggests, however, that son preference in India, when measured 
as ideally having more boys than girls, is decreasing over time and with 
higher education \citep{bhat03,pande07}.%
\footnote{
This measure of son preference is commonly used in the literature. 
See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
}

In the absence of prenatal sex determination, parents' only choice if they 
want a son is to try for another pregnancy as soon as possible after
the birth of a girl. 
Hence, in the absence of sex-selective abortions, son preference  
leads to a shorter duration until the next birth if the previous 
birth was a daughter  
\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
The resulting shorter spacing is thought to be associated with worse 
health outcomes for the girls 
\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter \citep{ben-porath76b,Das1987,Arnold1997,clark00}.

>>>>

The extent of son preference has been an important research area for 
decades and is as salient as ever.
Three approaches have been in widespread use in the literature:
birth spacing, parity progression, and sex ratio \citep{Leung1988}.
Before the availability of prenatal sex determination, parents' only choice 
if they wanted a son was to try for another pregnancy as soon as possible 
after the birth of a girl. 
In that case, son preference leads to a shorter spacing from the birth
of a daughter until the next birth   
\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
The resulting shorter spacing is thought to be associated with worse 
health outcomes for the girls 
\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter, resulting in a lower parity progression
with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}.

Sex ratio is the ratio of boys to girls measured for given ages, 
or, after the introduction of prenatal sex determination, at birth.
Deviation from the natural sex ratio is taken as an indication of sex preference
leading to differential mortality and/or use of prenatal sex selection.

India, for example, has seen dramatic increases in the males-to-females ratio 
at birth over the last three decades as access to prenatal sex determination 
expanded.%
\footnote{
See \citet{das_gupta97}, \citet{Sudha1999},
\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
India is not alone; both China and South Korea saw
significant changes in the sex ratio at birth over the same period \citep{Yi1993,park95}.
}

Recent research suggests, however, that son preference in India, when measured 
as ideally having more boys than girls, is decreasing over time and with 
higher education \citep{bhat03,pande07}.%
\footnote{
This measure of son preference is commonly used in the literature. 
See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
}
